---
title: "Final_customer analytics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
cat("\014")
```

```{r }
library(tidyverse)
library(readxl)
library(dplyr)
library(tidyr)
#install.packages('fastDummies')
library(fastDummies)
RawData = read_excel("Data Keywords.xls",sheet=1)
KeyWordCat = read_excel("Data Keywords.xls",sheet=2)
RawData$Date <- as.Date(RawData$Date)
names(RawData) <- make.names(names(RawData))
names(KeyWordCat) <- make.names(names(KeyWordCat))
df <- merge(RawData,KeyWordCat,by.x="Keyword.ID",by.y="KW.ID")
df = select(df,-Category)

# add variables 
## CPC - cost per click
df$CPC = df$Cost/df$Clicks
## CTR - click through rate
df$CTR = df$Clicks/df$Impressions
## Conversion Rate
df$Conv = df$Reservations/df$Clicks
## CPR - cost per reservation  CPC/Conversion
df$CPR = df$CPC/ df$Conv
head(df)
```


#df2$Target2 <- ifelse(prediction.testing$PredictResponseRate >=cutoff, 1, 0)
#str(df2)
#str(df)
# analysis on CTR 
#df2$CTR_seg <-  transform(df2, group=cut(CTR), breaks=c(-Inf,1, 2, 3, Inf),labels=c('<1', 1, 2, 3,'>4'))

# classification for attractive keywords

prediction.testing$Target2 <- ifelse(prediction.testing$PredictResponseRate >=cutoff, 1, 0)

results <- fastDummies::dummy_cols(df2, select_columns = c("Category.ID","Keyword.Type.ID"))
results$weekday <- weekdays(results$Date) 
results <- fastDummies::dummy_cols(results, select_columns = c("weekday"))
str(results)
results$weekend = results$weekday_Saturday+results$weekday_Sunday
linearmodel_click = lm(Clicks~ weekend+Average.Position + Impressions+ Category.ID_0+ Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+Keyword.Type.ID_0+ Keyword.Type.ID_1, data=results)
summary(linearmodel_click)

linearmodel_CPC = lm(CPC~ weekend+Average.Position + Impressions+ Category.ID_0+ Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+Keyword.Type.ID_0+ Keyword.Type.ID_1, data=results)
summary(linearmodel_CPC)

linearmodel_reservations = lm(Reservations~ weekend+Clicks+ Average.Position + Impressions+ Category.ID_0+ Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+Keyword.Type.ID_0+ Keyword.Type.ID_1, data=results)
summary(linearmodel_reservations)

linearmodel_cpr = lm(CPC~ Clicks+ weekend+ Average.Position + Impressions+ Category.ID_0+ Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+Keyword.Type.ID_0+ Keyword.Type.ID_1, data=results)
summary(linearmodel_cpr)
data you haven
what we want to find 
what we want to model
why 
how
str(results)

summary(linearmodel_reservations)

linearmodel_click = lm(Clicks~ `Average Position` + `Impressions`+ `Category ID_0`+ `Category ID_1` +`Category ID_2`+`Category ID_3` + `Category ID_4`+`Category ID_6`+`Keyword Type ID_0`+ `Keyword Type ID_1`, data=results)
names(results)
summary(linearmodel_click)
#head(results)

install.packages("caTools")
library(caTools)
install.packages("rpart")
library(rpart)
install.packages("rpart.plot")
library(rpart.plot)
install.packages("randomForest")
library(randomForest)

StevensTree = rpart(Clicks~ Average.Position + Impressions`+ `Category ID_0`+ `Category ID_1` +`Category ID_2`+`Category ID_3` + `Category ID_4`+`Category ID_6`+`Keyword Type ID_0`+ `Keyword Type ID_1`, method="class", data=results, minbucket=25)
prp(StevensTree)

RF = randomForest(Clicks~ Average.Position + Impressions+ Category.ID_0+ Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+Keyword.Type.ID_0+ Keyword.Type.ID_1, data=results, ntree=200, nodesize=15)

summary(RF)
names(results)
head(results)
results$
```
# group by with keyword
```{r} 
library(tidyr)     

RawData.groupby = 
  RawData %>%
  group_by(Keyword.ID) %>% 
  dplyr::summarise(
    Average.Position = mean(Average.Position,na.rm=TRUE),
    Impressions= sum(Impressions),
    Clicks= sum(Clicks),
    Cost= sum(Cost),
    Reservations=sum(Reservations)
  )

str(RawData)
df.groupby <- merge(RawData.groupby,KeyWordCat,by.x="Keyword.ID",by.y="KW.ID")
df.groupby = select(df.groupby,-Category)

head(df.groupby)
# add variables 
## CPC - cost per click
df.groupby$CPC = df.groupby$Cost/df.groupby$Clicks
## CTR - click through rate
df.groupby$CTR = df.groupby$Clicks/df.groupby$Impressions
## Conversion Rate
df.groupby$Conv = df.groupby$Reservations/df.groupby$Clicks
## CPR - cost per reservation  CPC/Conversion
df.groupby$CPR = df.groupby$CPC/ df.groupby$Conv


#do nothing
sum(df.groupby$Cost)
sum(df.groupby$Reservations)
table(df2$CPR)

# Face Value
df.groupby.facevalue = subset(df.groupby,df.groupby$CPR<=30)
## how many keywords left
tb = table(df.groupby.facevalue$Keyword.ID)
nrow(tb)
## total cost and reservation
sum(df.groupby.facevalue$Cost)
sum(df.groupby.facevalue$Reservations)
table(df.groupby$CTR)
mean(df.groupby$CTR)
# CTR
df.groupby.ctr = subset(df.groupby,df.groupby$CTR>=(sum(df.groupby$Click)/sum(df.groupby$Impressions)))
tb.ctr = table(df.groupby.ctr$Keyword.ID)
## how many keywords left
nrow(tb.ctr)
## total cost and reservation
sum(df.groupby.ctr$Cost)
sum(df.groupby.ctr$Reservations)
mean(df2$CTR)
table(df2$Conv>0)
df2$Conv
nrow(df2)

df.groupby[df.groupby$Keyword.ID == 89,]



# Analysis with tree model

#install.packages("rpart")
library(rpart)
#install.packages("rpart.plot")
library(rpart.plot)
#install.packages("randomForest")
library(randomForest)
#install.packages("rattle")
library(rattle)	

# notes: removed impression lower than 100 from data
df.tree.all = subset(df.groupby,Impressions>=100)
df.tree.all <- fastDummies::dummy_cols(df.tree.all, select_columns = c("Category.ID","Keyword.Type.ID","X2nd.Category.ID"))
## second categroy only use keyword count>=2
names(df.tree.all)


set.seed(1313)
## attractive critiera : low CPR lower than 30
df.tree.model1 = data.frame(df.tree.all)
df.tree.model1$Target <- ifelse(df.tree.model1$CPR <=30, 1, 0)

model1 = rpart(Target~ Average.Position+ Impressions + Category.ID_0 + Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+ Keyword.Type.ID_0 
+ X2nd.Category.ID_3+ X2nd.Category.ID_6+ X2nd.Category.ID_12+ X2nd.Category.ID_13+ X2nd.Category.ID_16+ X2nd.Category.ID_21+ X2nd.Category.ID_23+ X2nd.Category.ID_25+ X2nd.Category.ID_30+ X2nd.Category.ID_31+ X2nd.Category.ID_33+ X2nd.Category.ID_34+ X2nd.Category.ID_35+ X2nd.Category.ID_41+ X2nd.Category.ID_43+ X2nd.Category.ID_46+ X2nd.Category.ID_49+ X2nd.Category.ID_50+ X2nd.Category.ID_51+ X2nd.Category.ID_54+ X2nd.Category.ID_56+ X2nd.Category.ID_57+ X2nd.Category.ID_60+ X2nd.Category.ID_62+ X2nd.Category.ID_66+ X2nd.Category.ID_68+ X2nd.Category.ID_69+ X2nd.Category.ID_79+ X2nd.Category.ID_84+ X2nd.Category.ID_85+ X2nd.Category.ID_87+X2nd.Category.ID_92, method="class", data=df.tree.model1, minbucket=20)
prp(model1)
rattle::fancyRpartPlot(model1)
model1_nopositions = rpart(Target~ Category.ID_0 + Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+ Keyword.Type.ID_0 
+ X2nd.Category.ID_3+ X2nd.Category.ID_6+ X2nd.Category.ID_12+ X2nd.Category.ID_13+ X2nd.Category.ID_16+ X2nd.Category.ID_21+ X2nd.Category.ID_23+ X2nd.Category.ID_25+ X2nd.Category.ID_30+ X2nd.Category.ID_31+ X2nd.Category.ID_33+ X2nd.Category.ID_34+ X2nd.Category.ID_35+ X2nd.Category.ID_41+ X2nd.Category.ID_43+ X2nd.Category.ID_46+ X2nd.Category.ID_49+ X2nd.Category.ID_50+ X2nd.Category.ID_51+ X2nd.Category.ID_54+ X2nd.Category.ID_56+ X2nd.Category.ID_57+ X2nd.Category.ID_60+ X2nd.Category.ID_62+ X2nd.Category.ID_66+ X2nd.Category.ID_68+ X2nd.Category.ID_69+ X2nd.Category.ID_79+ X2nd.Category.ID_84+ X2nd.Category.ID_85+ X2nd.Category.ID_87+X2nd.Category.ID_92, method="class", data=df.tree.model1, minbucket=20)
prp(model1_nopositions)
rattle::fancyRpartPlot(model1_nopositions)

## attractive critiera : high CTR higher than 0.7% (overall average)
df.tree.model2 = data.frame(df.tree.all)
df.tree.model2$Target <- ifelse(df.tree.model1$CTR >=0.007, 1, 0)

model2 = rpart(Target~ Average.Position+ Impressions + Category.ID_0 + Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+ Keyword.Type.ID_0 
+ X2nd.Category.ID_3+ X2nd.Category.ID_6+ X2nd.Category.ID_12+ X2nd.Category.ID_13+ X2nd.Category.ID_16+ X2nd.Category.ID_21+ X2nd.Category.ID_23+ X2nd.Category.ID_25+ X2nd.Category.ID_30+ X2nd.Category.ID_31+ X2nd.Category.ID_33+ X2nd.Category.ID_34+ X2nd.Category.ID_35+ X2nd.Category.ID_41+ X2nd.Category.ID_43+ X2nd.Category.ID_46+ X2nd.Category.ID_49+ X2nd.Category.ID_50+ X2nd.Category.ID_51+ X2nd.Category.ID_54+ X2nd.Category.ID_56+ X2nd.Category.ID_57+ X2nd.Category.ID_60+ X2nd.Category.ID_62+ X2nd.Category.ID_66+ X2nd.Category.ID_68+ X2nd.Category.ID_69+ X2nd.Category.ID_79+ X2nd.Category.ID_84+ X2nd.Category.ID_85+ X2nd.Category.ID_87+X2nd.Category.ID_92, method="class", data=df.tree.model2, minbucket=20)
#prp(model1)
rattle::fancyRpartPlot(model2)
model2_nopositions = rpart(Target~  Category.ID_0 + Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+ Keyword.Type.ID_0 
+ X2nd.Category.ID_3+ X2nd.Category.ID_6+ X2nd.Category.ID_12+ X2nd.Category.ID_13+ X2nd.Category.ID_16+ X2nd.Category.ID_21+ X2nd.Category.ID_23+ X2nd.Category.ID_25+ X2nd.Category.ID_30+ X2nd.Category.ID_31+ X2nd.Category.ID_33+ X2nd.Category.ID_34+ X2nd.Category.ID_35+ X2nd.Category.ID_41+ X2nd.Category.ID_43+ X2nd.Category.ID_46+ X2nd.Category.ID_49+ X2nd.Category.ID_50+ X2nd.Category.ID_51+ X2nd.Category.ID_54+ X2nd.Category.ID_56+ X2nd.Category.ID_57+ X2nd.Category.ID_60+ X2nd.Category.ID_62+ X2nd.Category.ID_66+ X2nd.Category.ID_68+ X2nd.Category.ID_69+ X2nd.Category.ID_79+ X2nd.Category.ID_84+ X2nd.Category.ID_85+ X2nd.Category.ID_87+X2nd.Category.ID_92, method="class", data=df.tree.model2, minbucket=25)
#prp(model1)
rattle::fancyRpartPlot(model2_nopositions)



## attractive critiera : low CPR lower than 30 or high CTR higher than 0.7% (overall average)
df.tree.model3 = data.frame(df.tree.all)
df.tree.model3$Target <- ifelse(df.tree.model1$CPR <=30 | df.tree.model1$CTR >=0.007 , 1, 0)

model3 = rpart(Target~ Average.Position+ Impressions + Category.ID_0 + Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+ Keyword.Type.ID_0 
+ X2nd.Category.ID_3+x X2nd.Category.ID_6+ X2nd.Category.ID_12+ X2nd.Category.ID_13+ X2nd.Category.ID_16+ X2nd.Category.ID_21+ X2nd.Category.ID_23+ X2nd.Category.ID_25+ X2nd.Category.ID_30+ X2nd.Category.ID_31+ X2nd.Category.ID_33+ X2nd.Category.ID_34+ X2nd.Category.ID_35+ X2nd.Category.ID_41+ X2nd.Category.ID_43+ X2nd.Category.ID_46+ X2nd.Category.ID_49+ X2nd.Category.ID_50+ X2nd.Category.ID_51+ X2nd.Category.ID_54+ X2nd.Category.ID_56+ X2nd.Category.ID_57+ X2nd.Category.ID_60+ X2nd.Category.ID_62+ X2nd.Category.ID_66+ X2nd.Category.ID_68+ X2nd.Category.ID_69+ X2nd.Category.ID_79+ X2nd.Category.ID_84+ X2nd.Category.ID_85+ X2nd.Category.ID_87+X2nd.Category.ID_92, method="class", data=df.tree.model3, minbucket=20)
#prp(model1)
rattle::fancyRpartPlot(model3)
model3_nopositions = rpart(Target~  Category.ID_0 + Category.ID_1 +Category.ID_2+Category.ID_3 + Category.ID_4+Category.ID_6+ Keyword.Type.ID_0 
+ X2nd.Category.ID_3+ X2nd.Category.ID_6+ X2nd.Category.ID_12+ X2nd.Category.ID_13+ X2nd.Category.ID_16+ X2nd.Category.ID_21+ X2nd.Category.ID_23+ X2nd.Category.ID_25+ X2nd.Category.ID_30+ X2nd.Category.ID_31+ X2nd.Category.ID_33+ X2nd.Category.ID_34+ X2nd.Category.ID_35+ X2nd.Category.ID_41+ X2nd.Category.ID_43+ X2nd.Category.ID_46+ X2nd.Category.ID_49+ X2nd.Category.ID_50+ X2nd.Category.ID_51+ X2nd.Category.ID_54+ X2nd.Category.ID_56+ X2nd.Category.ID_57+ X2nd.Category.ID_60+ X2nd.Category.ID_62+ X2nd.Category.ID_66+ X2nd.Category.ID_68+ X2nd.Category.ID_69+ X2nd.Category.ID_79+ X2nd.Category.ID_84+ X2nd.Category.ID_85+ X2nd.Category.ID_87+X2nd.Category.ID_92, method="class", data=df.tree.model3, minbucket=10)
prp(model3_nopositions)
rattle::fancyRpartPlot(model3_nopositions)




df.groupby$cost.reservation = df.groupby$Cost/ df.groupby$Reservations
df.groupby[df.groupby$Keyword.ID == 89,]
table(df.groupby$CPR<10)
sum(df.groupby$Cost)/sum(df.groupby$Reservations)


```


df[which.max(df$Reservations),]
test = df[1:3,]
test
#results <- fastDummies::dummy_cols(df)
#results <- fastDummies::dummy_cols(df, select_columns = "Category ID")
#dataf <- dummy_cols(dataf, select_columns = 'rank')
head(df)
# analysis on Conversion Rate

linearmodel_click = lm(CPC~ `Average Position`+ Impressions + `Category ID` + `2nd Category ID` + `Keyword Type ID`, data=df)
summary(linearmodel_click)
cor(df$`Average Position`,df$Clicks)
cor(df$`Impressions`,df$Clicks)
str(df)
subset()

sort_impres sions.df <- hsb2[order(read) , ]
df[order()]

df

subset(df,df$`Keyword ID`==277)
df[which.min(df$CPC),]
df[which.max(df$CPC),]



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
